---
title       : Development Data Products
subtitle    : Final Project - Slidify
author      : YRY12 / August 24, 2014
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

-For the final project, I employed a emission data available from National Emissions Inventory (NEI), 
"http://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip". The NEI emissions is compiled by the  Environmental Protection Agency (EPA) with the aim to track emission in the atmosphere.

-In this analysis we focus in the visual analsys of emission of four type of vehicles (Non-road, Nonpoint,  On-road, and Point) in four years (1999, 2002, 2005, and 2008).

--- .class #id

## Summary data
This is summary the information of the data we use.

```{r, echo=FALSE}
setwd("C:/coursera/jhudatascience/developingprd/finalproject")
load("emission.rda")
summary(emission)
```

--- .class #id

## Example

The shiny app produces a chart bar for each of the four vehicles. Example:

```{r, echo=FALSE}
setwd("C:/coursera/jhudatascience/developingprd/finalproject")
load("emission.rda")
library(ggplot2)
    display_data <- emission[emission$type=="Non-road",]
    ggplot(display_data, aes(x=year, y=logpm25)) + guides(fill=F) +
    geom_bar(stat='identity') + ggtitle('Non-road Emissions') + ylim(0, 20) 
```

--- .class #id

## Github Repository

More details of this shinny app can be found at

https://github.com/yry12/devdataproducts

Slidify

https://github.com/yry12/devdataproduct_slidify

